\sffamily An EEG-based visual Brain-Computer Interface for gaze-free communication

### 2024-12-05 chapters/covert_align.tex
Proofread preface
Cover fold line and address, loop figure odd page

\chapter{Compensating \acs{erp} jitter for gaze-independence}%
\label{sec:covert-align}
\epigraph{``You see, but you do not observe!''}{Sherlock Holmes in  \\ \emph{A
Scandal in Bohemia -- Sir Arthur Conan Doyle}}
\publicationnote{This chapter was published as part of~\textcite{VanDenKerchove2024}.}

@@

\subsubsection{Decoders}%
\label{sec:covert-align/methods/decoders}
We compared \ac{wcble} and \ac{cble} as described in
\cref{sec:wcble/methods}, with their base classifier \ac{tlda} and with
Riemannian Geometry approaches that rely on spatial covariance as features.
Together with \ac{tlda}, Riemannian Geometry generally achieves state-of-the-art decoding
performance~\cite{Lotte2018}.
We implemented two Riemannian Geometry pipelines.
The first estimates shrunk covariances from the \acp{erp} filtered with 6 XDAWN
filters, projects these covariances to a tangent space, and classifies the
result using $L_2$-regularized logistic regression
(XDAWNCov-TS-LR)~\cite{Cecotti2017}.
Secondly, we adopted the pipeline from \textcite{Aydarkhanov2020}, as their work shows
favorable performance in the presence of single-trial \ac{erp} latency jitter.
Shrunk spatial covariance matrices were estimated from epochs that were
augmented by concatenating the average target and average non-target \ac{erp} as
extra channels, projected to tangent space, and classified using
$L_2$-regularized logistic regression (ERPCov-TS-LR).

>>>>

\chapter{Compensating \acs{erp} jitter for gaze-independence}%
\label{sec:covert-align}
\epigraph{``You see, but you do not observe!''}{Sherlock Holmes in  \\ \emph{A
Scandal in Bohemia -- Arthur C. Doyle}}
\publicationnote{This chapter was published as part of~\textcite{VanDenKerchove2024}.}

@@

\subsubsection{Decoders}%
\label{sec:covert-align/methods/decoders}
We compared the two latency-based methods \ac{wcble} and \ac{cble} as described in
\cref{sec:wcble/methods}, with their base classifier \ac{tlda} and with
Riemannian Geometry approaches that rely on spatial covariance as features.
Together with \ac{tlda}, Riemannian Geometry generally achieves state-of-the-art decoding
performance~\cite{Lotte2018}.
We implemented two Riemannian Geometry pipelines.
The first estimates shrunk covariances from the \acp{erp} filtered with 6 XDAWN
filters, projects these covariances to a tangent space, and classifies the
result using $L_2$-regularized logistic regression
(XDAWNCov-TS-LR)~\cite{Cecotti2017}.
Secondly, we adopted the pipeline from \textcite{Aydarkhanov2020}, as their work shows
favorable performance in the presence of single-trial \ac{erp} latency jitter.
Shrunk spatial covariance matrices were estimated from epochs that were
augmented by concatenating the average target and average non-target \ac{erp} as
extra channels, projected to tangent space, and classified using
$L_2$-regularized logistic regression (ERPCov-TS-LR).
